---
title: "Mouse_tracking_vol_2"
author: "Amalie Lysgaard Andersen"
date: "28/3/2019"
output: html_document
---

```{r setup, include=FALSE}

setwd("~/Library/Mobile Documents/com~apple~CloudDocs/4. Aarhus Universitet/4. Semester/3. Models for perception and action/5. Decisions in the hand/Mouse_tracking")
```

```{r data}
#df, long format data - The data we used the first week
load("MT_Pilot20190314.R") 

df <- subset(df, ID == unique(df$ID)[1] & GainLoss == unique(df$GainLoss)[1] & Trial == unique(df$Trial)[1] )
#df <- df[85:91,]
```

#calculate euclidian distance....
```{r}
correct_manualdist <- sum(sqrt(diff(df$Pos_x)^2 + diff(df$Pos_y)^2))
correct_manualdist

# 442 pixels: the lowest distance from start to end of trial --> this is the "right" distance
```


################

#same data but rearranged to fit the mousetrap package
```{r}
#mt, list object 
load("MTrap_Pilot20190314.R") 
```


#What does the data look like
```{r}
head(mt[[1]])

#time stamps
mt[[2]][1:10,1:10,1]

#what dimensions do I have?
names(mt[[2]][1,1,]) 

# data for one trajectory
head(mt[[2]][1,,])
```

#Calculate euclidian distance
```{r}
library("mousetrap")

# 
mt[[2]] <- mt_derivatives(mt[[2]]) 

#What did we get?
head(mt[[2]][1,,])

#3 dimensional data: we get x+y distance but also distance, velocity and acceleration for one trajectory
```

#calculate trial-wise/per trajectory measures (based on mt_id)
```{r}
measures <- mt_measures(mt[[2]])  
#what did we get?
head(measures) 

#data calculated in loads of measures
```



#compare manual distance measure
#although measures are already trial-by-trial we aggregate again over trial since mt_id is not in df
```{r}
#Aggregate: does the same as above, but we have the opportunity to select  what parts of the data we want represented --> we're aggregating the data!
per_trial <- mt_aggregate(measures, use2 = mt[[1]], use2_variables = c("ID", "GainLoss", "Trial", "Volatility")) #mt[1] --> data in element 1
head(per_trial)

mousetrap_dist <-per_trial$total_dist[match(paste0(df$ID[1], 
                                                   df$GainLoss[1], 
                                                   df$Trial[1]), 
                                            paste0(per_trial$ID, 
                                                   per_trial$GainLoss, 
                                                   per_trial$Trial))]

```

#what distance measures did we get?
```{r}
mousetrap_dist
# [1] 442.6289

correct_manualdist
# [1] 442.6289

mousetrap_dist == correct_manualdist
# [1] TRUE
```




#simple test on data aggregated per subject and conditions
#(I would usually not aggregate over trials but for the sake of simplicity...)
```{r}
per_subject <- mt_aggregate(measures, use2 = mt[[1]], use2_variables = c("ID", "GainLoss","TestCondition", "Volatility"))
per_subject_testgain <- subset(per_subject, GainLoss == "Gain" & TestCondition == 1)
head(per_subject_testgain)
```


#I just start with plotting a bit
```{r}
#PLOTTING TOTAL DISTANCE IN THE TWO CONDITIONS

library("ggplot2")
ggplot(per_subject_testgain, aes(x = total_dist, stat(density), color = Volatility)) +
  geom_freqpoly(binwidth = 40)
#log transformation would make it slightly more normal ()
ggplot(per_subject_testgain, aes(x = log(total_dist), stat(density), color = Volatility)) +
  geom_freqpoly(binwidth = 0.1)
```


#simplest test possible
```{r}
t.test(log(total_dist)~Volatility, data = per_subject_testgain, paired = T)  

# mean of the differences 
#             0.03210272 

#Uh very low corr
```





###Visualization
```{r}
mt_plot(mt[[2]])
mt_plot(mt[[2]], use = "trajectories", use2 = mt[[1]], facet_row = "Volatility", 
        facet_col= "GainLoss")
```





#Subsetting (can't make the mt_subset to work...)
#Easier data to play around with
```{r}
mtsubset_ids <- mt[[1]]$TestCondition == 1 & mt[[1]]$GainLoss == "Gain"
mtsub <- mt[[2]][mtsubset_ids,,]
mt_plot(mtsub, use = "trajectories", use2 = mt[[1]][mtsubset_ids,], facet_col = "Volatility")
```




#identifying and plotting 4 clusters
#it is necessary to have an equal number of observations per trajectory.
```{r}
spatial <- mt_spatialize(mtsub)
cluster_test <- mt_cluster(spatial, n_cluster = 4, use = "sp_trajectories")  #creating clusters and testing they difference

# CLUSTER PLOT
mt_plot(spatial, use="trajectories", use2 = cluster_test, facet_col="cluster")

```


HEATMAP YES
```{r}
mt_heatmap(mt[[2]], bounds = c(-400, -50, 400, 450))
```




